Blowship - Untraceable Low-Latency Message Transfer via a Central Server

### 2014-03-16 paper.tex
Makework good

\documentclass[twocolumn,11pt,english]{article}
\usepackage{comment}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{cite}
\usepackage{relsize}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage{pstricks}

\title{Blowship - Untraceable Instantaneous Message Transfer via a Central Server}
\date{}
\author{
  Carlyle, John\\
  \textit{jcarlyle@ucsc.edu}
  \and
  McDermott, Morgan\\
  \textit{mmcdermo@ucsc.edu}
}

@@

Traditional cryptography hides the message being sent from one party to another. This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: to whom the message is sent. Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers, cannot figure out the message's final destination. Many of these systems rely upon the fact that the user is accessing a constantly avaible resource, such as with Tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the recipient.

We present to the reader Untraceable Instantaneous Messaging, via a central server. Our message passing system is initiated by the browser, allowing a person to browse to one central location and conveniently use this service. A much different experience than with using many other P2P communication protocols. The central server is primarily used as an entrypoint into a network of peers. The peers are used to obsfucate who is sending messages to whom, allowing the clients to communicate with both private content and correspondant, all in as close to real time as possible given the constraints of the algorithms being used.

@@

\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{description}
\item[Penguin] 
  is any malicious Peer. A penguin can send false messages to the server. 
\item[Surge] 
  is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
\item[Proletariat] 
  is a group of colluding Penguins.
\item[The Fort] 
  is Surge and a Proletariat colluding. In this situation Surge could be generating new peers to act as Penguins in order to form The Fort.
\end{description}

\section{Previous Work}
The majority of research into anonymous communication uses decentralized P2P networks. In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server.

\subsection{Mixes}
Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies. Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}. They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email. Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for web data.

\subsection{Nym systems} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity. Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we develop in this paper.

\subsection{Private Information Retrieval} Private Information Retrieval (PIR) has been used to facilitate anonymous communication in a variety of ways. The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees. Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory.

\section{Privacy Goals}
The goal of this system is to provide a method for secure communication between parties through a central server with low latency and low communication overhead. We satisfy these requirements by assuming the intermediate server may be compromised. We define secure communication as thus \textbf{[6]}: FIX THIS CITE. Not sure which one it is.
\\\\\textbf{Communication Privacy:} Any party Eve cannot read the contents of intercepted messages sent between any two parties, Alice and Bob. 
\\\textbf{Participant Privacy:} This is also called \textbf{Unobservability} and \textbf{Untraceability}. Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ with a clear lower bound of $\epsilon > 1/N$. The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
\\\textbf{Destination Privacy:} Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.

\section{The Na\"ive Protocol}
Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, by having peers communicate with each other indirectly through the central server.

In P2P protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity. In this system we'll use terminology from Tor and call the chain of peers a message passes through a $circuit$. A pseudo-P2P circuit then consists of an alternating chain of peer-server and server-peer communications.

@@

\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. This could be done using a public keyserver of some kind, or perhaps they have exchanged keys in advance through some other channel. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge. (This can be done using private information retrieval)

Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow P_2 \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow S \rightarrow B$ by sending the following message to Surge: 
\\
Let \scriptsize$M = ID_A||E_{KRA}[ header || time || nonce || message ]$
\normalsize
\\Let \scriptsize$F_{ij}[x] = header||E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
\normalsize
\\
Alice sends: $F_{S1}[F_{S2}[...F_{nB}[ M ]]]$ to Surge.

@@

In this system, peers operate exactly as Mixes in the literature \cite{chaum-mix} . That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[something]]], as well (as we will discuss) by reordering and batching messages. 
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a peer, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{p_1 \ldots p_n\}$ talked to Bob.
\item\textbf{Collusion.} If $s$ peers collude with Surge to form The Fort, then The Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $p_1 ... p_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases exponentially. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob. If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.

@@

\subsection{Analysis of a simple message} 
Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob.

@@

The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers. 
\begin{center}
$\gamma = P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)}$
\\ $ \Rightarrow x = log( \gamma ) + n$
\end{center}
Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability:
\begin{center}
 $p(P_{AB} > \gamma) = \mathlarger{\sum}\limits_{i=\log(\gamma) + n}^n {n \choose i} \phi^i (1 - \phi )^{n-i}$

@@

Intuitively, Alice would be in an anonymity set of size 2 when $\gamma = 0.5$. This happens when all but one nodes are compromised: $x = log( 0.5 ) + n = n - 1$.

\begin{figure}[ht]
  \small
  \begin{tabular}{| l | l | l | l | l | l |}

    \hline
    $\phi$ & N & n & x & $E[P_{AB}]$ & $p(P_{AB} > 0.5)$ \\\hline
    0.8 & 1000 & 10 & 9 & 0.031 & 0.38\\
    0.8 & 10000 & 14 & 13 & 0.010 & 0.20\\
    0.8 & 100000 & 17 & 16 & 0.003 & 0.12\\
    \hline
  \end{tabular}
  \caption{Table 42.42 - Probabilities things are bad}
\end{figure}

As seen in table 42.42, the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$. If Surge believes $P_{AB} = 0.5$ given 10000 peers, then the probability distribution size $S = 1.93$.

If this level of security is unacceptable, the length of the circuit can be chosen based on an estimate of $\phi$ and an acceptable $p(P_{AB} > \gamma)$. Assuming $\gamma = 0.5$, then 
\begin{center}
$p(P_{AB} > 0.5)$ = $n\phi^{n-1} (1 - \phi ) + \phi^n $
\end{center}

@@

\includegraphics*[width=\linewidth]{gamma5graph.eps}

Given this graph it's clear that if the network is believed to be widely compromised, security can be made up for by choosing longer circuits. Although $\phi = 0.8$ makes $n = 10$ an unviable choice, at a circuit length of $n=20$ having $\phi = 0.8$ hardly affects the security.

\begin{comment}
  TODO: Apply PIR to obtain security guarantees even when $R \subset S$
\end{comment}
\subsection{Peers as Mixes}
As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities. Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions. 
A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages. Common attacks are variants of the $n - 1$, or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.

@@

However, using Private Information Retrieval, (first introduced by Chor and Goldreich \cite{pir}), it is possible to have Alice obtain this information without the server getting any information about the records she retrieved.

The trivial way of achieving this is to send Alice the entire database. Although this is actually used in systems like Tor, it isn't practical given a system with thousands or possibly millions of records.

The first Private Information Retrieval databases developed were  Information-Theoretical PIR (ITPIR), and operate by separating data between multiple servers. This model is fairly efficient, although it assumes the servers won't collude to discover user queries.

@@

\subsection{Using PIR For Directories}
To allow Alice to get information about which peers are online, their public keys, and the public keys of people she wishes to communicate with, we maintain two PIR databases.

The first is a database of peers currently online, indexable by an integer between 0 and $N$, the number of online peers. Alice chooses peers for her circuits by querying for random indexes in this database:
\\ \hfill\\ 
\begin{tabular}{| l | l | l |}
  \hline
  Record ID & Peer ID & Peer Public Key \\ \hline
  0 & 687542 & $pubkey_{687542}$  \\ \hline
  1 & 552455 & $pubkey_{552455}$  \\ \hline
  ... & ... & $...$  \\ \hline
  n & 432314 & $pubkey_{432314}$  \\ \hline
\end{tabular}

\hfill\\\hfill\\The second is a similar database, except that it contains all known peers and is indexable by a user's ID. Alice uses this database to obtain Bob's public key:

\hfill\\ 
\begin{tabular}{| l | l | l |}
  \hline
  Peer ID & Peer Public Key \\ \hline
  909787 & $pubkey_{909787}$  \\ \hline
  424566 & $pubkey_{424566}$  \\ \hline
  ... & $...$  \\ \hline
  432314 & $pubkey_{432314}$  \\ \hline
\end{tabular}

\subsection{Peer Discovery}
Using the model described above, peer discovery is efficient for users.  Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

@@

In our system, however, a compromised Surge is disincentivized from lying about which peers are online. Consider a situation in which Alice wishes to send a message to Bob. If Surge doesn't report any non-colluding peers as online, then Alice won't send any messages to Bob since he appears to be offline. If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits.

@@

 Assuming that Surge can't lie about real peers being online (as discussed previously in Peer Discovery), Bob simply needs to ask random peers to query Surge for Bob's public key and send him the result. Requests sent to peers colluding with Surge could be faked, but Bob can send enough requests to gain any level of confidence he wishes that his key is being correctly distributed.

>>>>

\documentclass[twocolumn,11pt,english]{article}
\usepackage{comment}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{cite}
\usepackage{relsize}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage{pstricks}
\usepackage{pgfplots}

\title{Blowship - Untraceable Low-Latency Message Transfer via a Central Server}
\date{}
\author{
  Carlyle, John\\
  \textit{jcarlyle@ucsc.edu}
  \and
  McDermott, Morgan\\
  \textit{mmcdermo@ucsc.edu}
}

@@

Traditional cryptography hides the message being sent from one party to another. This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: the connection between sender and recipient.

Much work has been done to build networks that can obscure this connection by passing the message through a series of peers in such a way that no peer, or even large group of peers, can determine its destination. Many of these systems route the message through dedicated peers that are always online (as with Mix systems \cite{chaum-mix}, like the popular Tor\cite{tor-design} anonymity system). Many of these systems are designed to relay email and as such have high latency (as in \cite{minion-design}, although there are systems like Tor designed specifically to have low latency.

In most cases, these systems are highly decentralized. In Tor for example, the relay servers used are chosen by the client \cite{tor-design}, and the only ``central authority'' are the trusted directory servers. In this paper we explore building a highly centralized system, for use in cases where decentralization is difficult and to explore possible benefits.

Current browsers have limited P2P communication capability - currently, they only have the ability to facilitate P2P distribution of media like video \cite{daoust2012towards}, and can't communicate with general purpose messages. For this reason, there are no pure P2P anonymization networks that operate at the browser level without using plugins.

We present to the reader Untraceable Low-Latency Messaging via a Central Server. Our message system is accessed via the browser, allowing a person to browse to one central location and conveniently use this service, rather than using an external program for anonymity as with existing P2P services. The central server is acts as an intermediary and facilitator for the network of peers using it. The peers are used to obsfucate who is sending messages to whom, allowing the clients to maintain anonymity and message security, in as close to real time as possible.

\section{Previous Work}
The majority of research into anonymous communication uses decentralized P2P networks. In our work, we develop a centralized anonymous communication network using principles and protocols from these decentralized systems.

\subsection{Mixes}
Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies\cite{chaum-mix}. Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}. In his protocol, mixes encrypt messages using public-private key cryptography so that incoming and outgoing messages have different content. For further security, messages have a fixed size, and mixes reorder messages before relaying them.

 Mixes have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email. Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for data.

Some systems use a fixed route of Mixes (as in MixMinion), while others allow clients to choose their own route through the mixes (as in Tor).

The anonymity mixes provide depends on many factors and was thoroughly analyzed by Serjantov in~\cite{trickle02}. In our system we use peers in the network as mixes, and will analyze their security using the known attacks that Serjantov presents (See Section~\ref{sec:PeersAsMixes} for a more in depth discussion).

\subsection{Nym systems} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity \cite{sassaman:wpes2005}. Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient. Our paper implements exactly this forward channel, and so could easily be coupled with a Nym system.

\subsection{Private Information Retrieval}

Private Information Retrieval, first introduced by Chor and Goldreich \cite{pir}, allows a user to access information from a database without the database server learning the user's query.

The trivial way of achieving this is to send the user the entire database. Although this is actually used in systems like Tor\cite{tor-design}, it may not be practical given a database with thousands or possibly millions of records.

The first Private Information Retrieval databases developed were  Information-Theoretical PIR (ITPIR), and operate by separating data between multiple servers\cite{pir}. This model is fairly efficient, although it assumes the servers won't collude to discover user queries.

In all known PIR systems, query anonymity comes at a cost. It has been shown that the database must perform an $O(n)$ operation to respond to each query\cite{CPIR}, where $n$ is the size of the database. If this weren't the case, the database wouldn't touch every bit in the database to respond to a query and would gain some information about the query itself.

Additionally, there is communication overhead in all known PIR systems. Responses to queries are usually polynomial or polylogarithmic in $n$ \cite{CPIR} \cite{pir}.

Private Information Retrieval has been used to facilitate anonymous communication in a variety of ways. The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees. Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory. In our paper, we use PIR for directory services and investigate the possibility of using it for anonymous communication.

@@

\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{description}
\item[Penguin] 
  is any malicious Peer. A penguin can send false messages to the server. 
\item[Surge] 
  is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
\item[Proletariat] 
  is a group of colluding Penguins.
\item[The Fort] 
  is Surge and a Proletariat colluding. Surge could also form the Fort by generating artificial peers to act as Penguins.
\end{description}

\section{Privacy Goals}
The goal of this system is to provide a method for secure communication between parties through a central server with low latency and low communication overhead. We satisfy these requirements by assuming the intermediate server may be compromised. We define secure communication as:
\begin{enumerate}
\item\textbf{Communication Privacy:} Any party Eve cannot read the contents of intercepted messages sent between any two parties, Alice and Bob. 
\item\textbf{Untraceability:} This is also called \textbf{Unobservability}. Our definition is that any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given a chosen $\epsilon$ (with a clear lower bound of $\epsilon > 1/N$). The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
\end{enumerate}
\section{The Na\"ive Protocol}
Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, having peers communicate with each other indirectly through the central server.

In P2P protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity. In this system we'll use terminology from Tor\cite{tor-design} and call the chain of peers a message passes through a $circuit$. A pseudo-P2P circuit then consists of an alternating chain of peer-server and server-peer communications.

@@

\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. This could be achieved using our directory service as outlined in Section~\ref{sec:PIRDirectories}, or by exchanging keys in advance through some other channel. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge (This again can be done using the service in Section~\ref{sec:PIRDirectories}).

Alice can then send a message to Bob that will follow the path 
\\$A \rightarrow P_1 \rightarrow S \rightarrow P_2 \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow S \rightarrow B$ 
She sends this message by wrapping the initial data in successive layers of message headers and encryption as in Figure~\ref{messageStructure}.
\\
\begin{figure}[h]
Let \scriptsize$M = ID_A||E_{KRA}[ header || time || nonce || message ]$
\normalsize
\\Let \scriptsize$F_{ij}[x] = header||E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
\normalsize
\\
Final Message: $F_{S1}[F_{S2}[...F_{SB}[ M ]]]$
\caption{Message Structure}
\label{messageStructure}
\end{figure}

@@

In this system, peers operate exactly as Mixes in the literature \cite{chaum-mix} . That is, they prevent traffic correlation by removing a layer of encryption, as well (as we will discuss) by reordering and batching messages.

This system is designed so that without collusion from Surge, Penguins or a Proletariat are powerless to do anything but to delay or fail to forward messages. They don't know the ID of the next person they are forwarding the message to (since it's encrypted with the server's key), and obtain no other information when forwarding messages. 
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a peer, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{p_1 \ldots p_n\}$ talked to Bob.
\item\textbf{Collusion.} If $s$ peers collude with Surge to form The Fort, then The Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $p_1 ... p_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases dramatically. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB}$, the probability that Alice is talking to Bob, is $> 1/6$. If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ (if $n \subset s$), but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.

@@

\subsection{Peers as Mixes}
\label{sec:PeersAsMixes}
As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities. Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions. 
A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages. Common attacks are variants of the $n - 1$, or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.

In our case, Surge can bypass the benefits obtained from turning peers into 2-Threshhold mixes by delivering one of his own false message-forward-requests along with every real message sent to each peer, so he can disregard one branch and essentially remove the anonymity gained from each hop in the circuit.

\subsection{Anonymity inside The Fort} 
Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob when Surge colludes with Penguins to form The Fort.

@@

The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$, gives reasonable intuition into the \textit{worst-case} security of the system considering passing messages through circuits of peers. It can be interpreted as the probability that Alice has been ``found out'' to some specified degree.

If we assume that Alice is the ``prime suspect'', and that all other peers have a uniform distribution of probability assigned to them, we get that $S$ (the number of bits the attacker still needs to gain) is:

\begin{center}
$-S = (1 - \gamma) \log(\frac{1-\gamma}{N - 1}) + \gamma \log(\gamma)$
\end{center}

To gain an intuition about what values of $\gamma$ mean, we can then plot $S$ for various values of $\gamma$
\begin{figure}[h!]
  \begin{tikzpicture}[scale=0.8]
    \begin{axis}[
      xlabel=$\gamma$
      ,ylabel = $(1-\phi)N$
      ,zlabel = $S$
      ,z label style = {rotate=270}
      ,ztick = {0,5,...,25}
      ,ytick = {100, 1000, 10000, 100000}
      ,ymode = log
      ,log basis y={10}
      ]
      \addplot3[surf, mesh/interior colormap={blueblack}{color=(orange) color=(white)},
      colormap/blackwhite, domain=0:1, y domain =100:100000, range = 0:20] { -1 * (((1 - x) * log2((1 - x)/(y-1)) + x * log2(x) )) };
    \end{axis}
  \end{tikzpicture}  
  \caption{Relating $\gamma$ and $S$}
  \label{gammaS}
\end{figure}

As we can see in Figure~\ref{gammaS}, having additional peers in the network (higher $N$ values) only helps increase Alice's anonymity ($S$ value) when $\gamma$ is small. That is, having more peers in the network doesn't really mitigate the security lost if Surge already believes that Alice sent a message with probability $0 \ll \gamma < 1 $.

\subsection{Likelihood of the worst-case}
We'd like to know how likely the worst-case ($p(P_{AB} > \gamma)$) scenario is given the circuit length chosen by Alice.

If we let $x$ be the number of compromised peers Alice must choose such that $p(P_{AB} > \gamma)$, we obtain: 
\begin{center}
$\gamma = P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)}$
\\ $ \Rightarrow x = log( \gamma ) + n$
\end{center}
Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability:
\begin{center}
 $p(P_{AB} > \gamma) = \mathlarger{\sum}\limits_{i=\log(\gamma) + n}^n {n \choose i} \phi^i (1 - \phi )^{n-i}$

@@

Intuitively, Alice would be in an anonymity set of size 2 when $\gamma = 0.5$. This happens when all but one nodes are compromised, as indicated by our derived value $x = log( 0.5 ) + n = n - 1$.

\begin{figure}[h]
  \small
  \begin{tabular}{| l | l | l | l | l | l |}

    \hline
    $\phi$ & N & n & x & $E[P_{AB}]$ & $p(P_{AB} > 0.5)$ \\\hline
    0.8 & 1000 & 10 & 9 & 0.031 & 0.38\\
    0.8 & 10000 & 14 & 13 & 0.010 & 0.20\\
    0.8 & 100000 & 17 & 16 & 0.003 & 0.12\\
    \hline
  \end{tabular}
  \caption{Probability of the worst-case}
  \label{WorstCaseTable}
\end{figure}

As seen in Table~\ref{WorstCaseTable} , the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$. For reference, if Surge believes $P_{AB} = 0.5$ given the 2000 uncompromised peers, then the probability distribution size $S = 1.93$.

\subsection{Longer Circuits}
If this level of security is unacceptable, the length of the circuit can be chosen based on an estimate of $\phi$ and an acceptable $p(P_{AB} > \gamma)$. Assuming $\gamma = 0.5$, then 
\begin{center}
$p(P_{AB} > 0.5)$ = $n\phi^{n-1} (1 - \phi ) + \phi^n $
\end{center}

@@

\begin{figure}[h]
\includegraphics*[width=\linewidth]{gamma5graph.eps}
\caption{$p(P_{AB} > 0.5)$ given $n$ and $\phi$}
\label{gamma5graph}
\end{figure}

Given Figure~\ref{gamma5graph} it's clear that if the network is believed to be widely compromised, security can be made up for by choosing longer circuits. Although $\phi = 0.8$ makes $n = 10$ an unviable choice, at a circuit length of $n=20$ having $\phi = 0.8$ barely increases the likelihood of the worst-case.

\begin{comment}
  TODO: Apply PIR to obtain security guarantees even when $R \subset S$
\end{comment}

@@

However, using Private Information Retrieval, it is possible to have Alice obtain this information without the server getting any information about the records she retrieved.

@@

\subsection{Using PIR For Directories}
\label{sec:PIRDirectories}
To allow Alice to get information about which peers are online, their public keys, and the public keys of people she wishes to communicate with, we maintain two PIR databases.

The first is a database of peers currently online (Figure~\ref{onlinePeerDB}), indexable by an integer between 0 and $N$, the number of online peers. To reduce the number of PIR requests, we redundantly include the public keys in this database. Alice chooses peers for her circuits by querying using random indexes in this database:

\begin{figure}[ht]
  \centering
\begin{tabular}{| l | l | l |}
  \hline
  Record ID & Peer ID & Peer Public Key \\ \hline
  0 & 687542 & $pubkey_{687542}$  \\ \hline
  1 & 552455 & $pubkey_{552455}$  \\ \hline
  ... & ... & $...$  \\ \hline
  $N$ & 432314 & $pubkey_{432314}$  \\ \hline
\end{tabular}
\caption{The Online-Peer Database}
\label{onlinePeerDB}
\end{figure}

The second is a similar database (Figure~\ref{peerKeyDB}), that contains all known peers (online and offline) and is indexable by a user's ID. Alice uses this database to lookup the public keys of message recipients by their peer ID (which she can't do in the first database).

\begin{figure}[ht]
  \centering
\begin{tabular}{| l | l | }
  \hline
  Peer ID & Peer Public Key  \\ \hline
  909787 & $pubkey_{909787}$ \\ \hline
  424566 & $pubkey_{424566}$ \\ \hline
  ... & ... \\ \hline
  432314 & $pubkey_{432314}$  \\ \hline
\end{tabular}
\caption{The Peer Key Database}
\label{peerKeyDB}
\end{figure}

\subsection{Peer Discovery}
\label{sec:PeerDiscovery}
Using the model described above, choosing random peers for use in a circuit is efficient for users.  Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

@@

In our system, however, a compromised Surge is disincentivized from lying about which peers are online. Consider a situation in which Alice wishes to send a message to Bob. If Surge doesn't report any non-colluding peers as online, then Alice won't send any messages to Bob since he appears to be offline. If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits. Since Surge doesn't know that Alice and Bob are communicating beforehand, he is forced to either include or exclude all non-colluding peers from the online-peers database as a whole.

@@

 Assuming that Surge can't lie about real peers being online (as discussed in Section~\ref{sec:PeerDiscovery}), Bob simply needs to ask random peers to query Surge for Bob's public key and send him the result (We will call this \textbf{Auditing}). Requests sent to peers colluding with Surge could be faked, but Bob can send enough requests to gain any level of confidence he wishes that his key is being correctly distributed.
